%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.

\documentclass[]{deedy-resume-openfont}


\begin{document}

\lastupdated

\begin{textblock}{60}(0,0)
\color{date}\fontspec[Path = fonts/raleway/]{Raleway-Bold}\fontsize{8pt}{10pt}\selectfont 
*Eligible to work in USA(Citizen)
\end{textblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Mukul}{Hase}{ \urlstyle{same}\underline{\url{https://mukulhase.com}} | \href{mailto:mukulhase@gmail.com}{\underline{mukulhase@gmail.com}} | +1 ‪(425) 470-3076 / +(91)-9652743554
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIIT Hyderabad}
\descript{Bachelor's in Computer Science \& Engineering}
\location{Grad June 2018 | Hyderabad, India\\ CGPA: 8.34/10}
\sectionsep
\subsection{Narayana Junior College}
\location{Grad. May 2014|  Hyderabad, India\\ Percentage: 93}
\sectionsep
\subsection{Delhi Public School}
\location{Grad. May 2012|  Hyderabad, India\\ CGPA: 10/10}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{@{}lll}
2017	     & 1\textsuperscript{st} Place  & \textbf{\underline{\href{https://www.nbo.om/en/Pages/Competitions/NBO-Hackathon.aspx}{NBO Hackathon}}}\\
2016	     & 2\textsuperscript{nd} Place & \textbf{\underline{\href{https://www.acadaccelerator.com/}{MS Code.Fun.Do}}}\\
2018         & Dean's List  & IIIT 4\textsuperscript{th} Year\\
2016	     & Dean's List  & IIIT 2\textsuperscript{nd} Year\\
2015	     & Dean's List  & IIIT 1\textsuperscript{st} Year\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages (Advanced):}
 Python \textbullet{} Javascript (\& variants) \\
\location{Languages (Proficient):}
Java \textbullet{} C++
\textbullet{} Swift 
\textbullet{} Obj-C
 \textbullet{} Racket \textbullet{} Rails \textbullet{} C \textbullet{} PHP \textbullet{} Assembly  \textbullet{} Shell \textbullet{} Matlab \textbullet{} CSS
\textbullet{} Scheme   \\
\location{Familiar Technologies:}
React \textbullet{} OpenCV \textbullet{} AngularJS \textbullet{} MySQL \textbullet{} Postgres \textbullet jQuery \textbullet{} NumPy \textbullet{} Django \textbullet{} Android
\textbullet{} Cordova/Ionic \textbullet{} Git \textbullet{} Unreal Engine
\textbullet{} Chrome Extensions \textbullet{} PyQt \textbullet{} PyPI \textbullet{} Socket Programming \textbullet{} Keras \textbullet{} iOS \textbullet{} MeteorJS \textbullet{} React Native
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{UnderGraduate}
Computer Vision \\
Statistical Methods in AI \\
Data Structures \\
Complexity and Advanced Algorithms \\
Game Design and Engineering \\
Artificial Intelligence \\
Computer Networks \\
Operating Systems \\
Database Systems \\
Distributed System \\
Functional Programming \\
Principles of Information Security\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Software developer 2 at \href{https://microsoft.com/}{\underline{Microsoft}} }\\
\location{June 2018 – Current | Hyderabad, India}
\descript{Whiteboard sharing feature in Microsoft Teams}
Developing UI/UX in their Desktop App. (React, Graphql, Electron, Apollo)\\
\descript{End-to-end development of edge-based computer vision models for Document Cleanup, Cropping and Classification}
\textbullet Created a parametric system to generate realistic synthetic images of documents. (Used for training and scoring)
\textbullet Wrote various Python scripts for data collection, filtering, processing datasets \textbullet Created a pipeline for data-collection and training on AML \textbullet Created different voting, annotation and analysis tools.  \textbullet Ported desktop models to ONNX/CoreML/TFlite and implemented models on Native Android \& iOS. \\
\descript{Native Mobile App Development (Android and IOS) in Office Lens}
\textbullet  Worked on the Camera stack \textbullet  OfficeLens Re-architecture (Kotlin) \textbullet  Wrote GPU Shaders (Metal \& OpenGLES) \textbullet  Performance improvements on document deletion/updation times (10x)
\textbullet Created custom UI Animations.
\sectionsep

\runsubsection{SWE Intern at \href{https://freeagent.network/}{\underline{FreeAgent Software}} } (Bay Area startup) \\
\location{May 2017 – July 2017 | Saratoga, CA}
Worked with full-stack web technologies like React, GraphQL, Sequelize, Express, Apollo. \textbullet Was able to quickly ramp up on codebase and provide my first POC within a week.
\textbullet Built a merge feature. In the process, I smoothly handled a complete codebase refactor when switching database key from incremental ID to UUIDv4 ID.
\textbullet End to End creation of filtering system. Backend: Queries, APIs , Frontend: HOC, UI

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{ Python library for WhatsApp Web }\\
\descript{Widely Used 1500+ stars}
\textbf{\href{https://github.com/mukulhase/WhatsAPI}{[\underline{github}]}} Capable of running bots to respond to Whatsapp messages while the phone is able to independently operate. Deployed on PyPI.
\sectionsep

\runsubsection{ Twinder (Ionic App) }
\descript{Microsoft Code-Fun-Do Winner}
Localised and personalised tweet feed with sources and reference suggested based on tweet’s context. Swipe left to discard, right to read more(Tinder).
\sectionsep

\runsubsection{ 3-Sweep }
\descript{ Computer Vision desktop application. }
\textbf{\href{https://github.com/mukulhase/3-Sweep-Library}{[\underline{github}]}} Desktop application which let's you drag-select objects(like in Photoshop), and manipulate your 2D image in 3D
\sectionsep

\runsubsection{ Pebble Messenger } \\
\descript{ Shake2talk over Facebook chat on smart watch }
260 Users. MeteorJS Implementation involved handling multiple active facebook sessions on one AWS server and smartly fetching messages.
\sectionsep

\runsubsection{ Facebook Chatbot(known as Cleverfb) }

\descript{Chrome Extension to simulate user typing}
\textbf{\href{https://github.com/NMBL/CleverFB}{[\underline{github}]}} Users can use this on their friends to take over their conversation. Deployed as a chrome extension on the chrome web-store. 55 weekly users on average(Made without use of messenger API).
\sectionsep 

% \runsubsection{ Price-Comparison system }

% \descript{Price-Comparison system for Shoppersexpress.in}
% \textbf{\href{http://mukulhase.com/Comparison/project/Project_Files/index.html}{[link]}} Designed a unique backend-free way to scrape data from multiple online stores(Flipkart, Amazon, Snapdeal) using iframes, proxies etc).
% \sectionsep

% \runsubsection{ 2-D Virtual Clothes fitter }

% \descript{An 2D image  approach for virtual clothes fitting}
% A user takes a photo of himself/herself and virtually tries on template clothes available on any e-commerce websites. ~ Flask, Matlab(For image processing)
% \sectionsep

% \runsubsection{ Election portal using “Single Transferable Vote” }

% \descript{Used for college parliament elections \textbf{\href{github.com/mukulhase/STVElection}}{[github]}}
% \sectionsep

% \runsubsection{ IIIT’s fest(Felicity) website and MUN website } \\
% Website Coordinator: \textbf{\href{http://felicity.iiit.ac.in/}{http://felicity.iiit.ac.in/}} \\
% USG Technology: \textbf{\href{https://mun.iiit.ac.in}{https://mun.iiit.ac.in}}
% \sectionsep

\runsubsection{ Misc. Projects } \textbullet
\href{https://mukulhase.com/ThreeJSCarrom/}{\underline{Feature-filled Webgl 3D Game}} \textbullet  IIIT’s event portal, Gives everyone a personalized calendar based on their “groups”, integrated with college’s LDAP authentication. \textbullet Ultimate\textbf{} TicTacToe AI Solver \textbullet File Downloading Server(TCP/UDP) \textbullet Shell in C

\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}